\bf ISODS: An ISODATA-Based Initial Centroid Algorithm

### 2021-01-09 paper/paper.tex
paper revision 1

\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{abstract}
      \noindent 
      Iterative Self-Organizing Data Analysis Technique (ISODATA) is a
      clustering algorithm based on K-Means that intends to find the correct
      number of clusters through merging and splitting. Compared to K-Means, the
      ISODATA algorithm should be resilient to initial cluster centers. However,
      ISODATA is also sensitive to initial cluster centers which impacts the
      performance of the algorithm. This work proposes using the ISODATA
      approach of splitting clusters to select quality initial cluster centers.
      The proposed approach is evaluated on several benchmark UCI datasets as
      well as the Salinas-A hyperspectral image dataset. The results are
      evaluated using standard clustering evaluation parameters. \\
      {\bf Keywords :} Clustering, ISODATA, Initial Centroids, Remote Sensing
\end{abstract}

@@

Unsupervised learning is a machine learning technique used when the learning
algorithm has no pre-existing labels and looks for patterns in the data set with
minimum human supervision and without external guidance. In contrast to
supervised learning, where a training set of inputs and observations are given
to the method, unsupervised learning uses only the inputs and should find an
interesting pattern in the data set. Two main approaches are used in
unsupervised learning, named principal component \cite{Mallapragada2018} and
cluster analysis \cite{Xu2015}. In the clustering method, unlabeled and unsorted
data points are grouped and segmented according to similarities and differences
to find structure in the inputs, group it into meaningful clusters, and
understand the data set better. There are different algorithms for Clustering,
such as K-Means, fuzzy C-Means, ISODATA \cite{Ball1965}, and so on. In the
K-Means algorithm, the goal is to minimize the sum of the squared distances
points have in the data set from its center. The problem with the K-Means
algorithm is that it requires a priori knowledge about the number of classes in
the data set, and choosing the cluster centers randomly may not result in
optimal partitioning of the data set.

@@

The K-Means algorithm is an unsupervised clustering algorithm and aims to
partition $N$ observations into $K$ clusters [CITE]. Data points in the same
cluster are very similar to each other and have less variation compared to data
points assigned to other clusters. The user defines $K$, the number of expected
clusters. Following is a description of the K-Means algorithm:

@@

For selecting the initial cluster centers in \textbf{Step 1}, there are two
standard methods: Random Centers, and K-Means++ [CITE]. In Random Centers, $K$
samples are randomly chosen from the dataset to serve as the initial cluster
centers. In K-Means++, $1$ sample is randomly chosen from the dataset to serve
as the initial cluster center. Then, $K-1$ samples are iteratively selected,
where the probability of a sample being chosen as a cluster center is the
distance of the sample from previously chosen centers [CITE]. The K-Means
algorithm is susceptible to initial starting cluster centers, where different
initial values can result in a different classification.

@@

ISODATA is another frequently used clustering algorithm and is based on the
K-Means algorithm. Like K-Means, cluster centers are iteratively updated and
reassigned to the samples in the dataset. However, ISODATA determines the number
of clusters dynamically and allows for a different number of cluster centers. In
contrast, the K-Means algorithm requires a fixed user-set parameter of the
number of expected clusters. The advantage found within ISODATA allows for
discovery of a different number of clusters, which is achieved through
discarding clusters with a small number of member samples, and merging and
splitting clusters that meet certain parameters. There are three main ISODATA
parameters:

@@

There are some disadvantages to the ISODATA algorithm. First, it is sensitive to
the parameters $\theta n$, $\theta e$, and $\theta c$. These parameters should
be fine-tuned for optimal performance based on the attributes of the dataset
being tested. In addition, similar to K-Means, it is sensitive to initial
cluster centers, although less so than K-Means due to the extra processes of
discarding, splitting, and merging. The initial centroids can affect both the
quality of clusters produced and the number of iterations required to converge
      [CITE].

@@

\begin{itemize}
      \item \textbf{Step 1:} Choose $1$ observation as a cluster center from the
            dataset.
      \item \textbf{Step 2:} Assign each element of the dataset to the cluster
            based on the minimum distance from the cluster center.
      \item \textbf{Step 3:} Re-calculate new cluster centers for each cluster
            by computing the mean of all patterns assigned to each cluster.
      \item \textbf{Step 4:} If the number of clusters is equal to $K$, then the
            process is terminated. If the number of clusters is greater than
            $K$, then the clusters with the fewest members is discarded, and the
            algorithm moves to \textbf{Step 2}.
      \item \textbf{Step 5:} Calculate the standard deviation of each cluster in
            each dimension. Then, split each cluster along the dimension with
            the greatest standard deviation.
\end{itemize}

@@

\begin{table}[ht]
      \begin{tabular}{ |p{1.25cm}||p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm}|}
            \hline
            \multicolumn{7}{|c|}{\textbf{ISODATA}}                               \\
            \hline
            Init. & Iter.  & Clusters & ARI             & RI    & MI    & HI     \\
            \hline
            \multicolumn{7}{|c|}{\textit{Iris}}                                  \\[1ex]
            ISODS & 13.46  & 2.599    & \textbf{0.646}  & 0.826 & 0.173 & 0.653  \\
            KM++  & 15.43  & 2.544    & 0.628           & 0.816 & 0.184 & 0.631  \\
            Rand  & 11.90  & 2.41     & 0.607           & 0.802 & 0.198 & 0.604  \\
            \hline
            \multicolumn{7}{|c|}{\textit{Glass (Normalized)}}                    \\[1ex]
            ISODS & 3.19   & 1.066    & \textbf{0.0018} & 0.266 & 0.734 & -0.468 \\
            KM++  & 4.02   & 1.028    & 0.0011          & 0.265 & 0.735 & -0.470 \\
            Rand  & 3.69   & 1.055    & 0.0013          & 0.266 & 0.733 & -0.467 \\
            \hline
            \multicolumn{7}{|c|}{\textit{Wine}}                                  \\[1ex]
            ISODS & 9.16   & 1.836    & \textbf{0.313}  & 0.618 & 0.382 & 0.236  \\
            KM++  & 8.76   & 1.816    & 0.307           & 0.612 & 0.388 & 0.224  \\
            Rand  & 9.26   & 1.810    & 0.304           & 0.608 & 0.391 & 0.217  \\
            \hline 
            \multicolumn{7}{|c|}{\textbf{K-Means}}                               \\
            \hline
            \multicolumn{7}{|c|}{\textit{Iris}}                                  \\[1ex]
            ISODS & 2.29   & 3        & \textbf{0.623}  & 0.833 & 0.167 & 0.667  \\
            KM++  & 4.149  & 3        & 0.584           & 0.811 & 0.189 & 0.621  \\
            Rand  & 29.402 & 3        & 0.569           & 0.797 & 0.203 & 0.593  \\
            \hline
            \multicolumn{7}{|c|}{\textit{Glass (Normalized)}}                    \\[1ex]
            ISODS & 5.651  & 6        & 0.164           & 0.665 & 0.335 & 0.329  \\
            KM++  & 4.866  & 6        & \textbf{0.173}  & 0.643 & 0.357 & 0.285  \\
            Rand  & 77.178 & 6        & 0.151           & 0.634 & 0.366 & 0.268  \\
            \hline
            \multicolumn{7}{|c|}{\textit{Wine}}                                  \\[1ex]
            ISODS & 3.145  & 3        & \textbf{0.882}  & 0.947 & 0.053 & 0.895  \\
            KM++  & 5.388  & 3        & 0.839           & 0.926 & 0.074 & 0.851  \\
            Rand  & 24.775 & 3        & 0.834           & 0.920 & 0.080 & 0.840  \\
            \hline
      \end{tabular}
      \caption{UCI benchmark dataset results averaged over 1000 iterations of
            ISODATA and K-Means comparing three different initial cluster center
            algorithms (\textit{Init.}). Results in the table contain
            information on average iterations required (\textit{Iter.}), average
            number of clusters created (\textit{Clusters}), and validity
            measures.}
      \label{tab:ucitable}
\end{table}

@@

To evaluate the cluster results, external cluster validation measures are used.
We utilize pair-counting measures which rely on counting matching pairs between
two sets of data to determine agreement and disagreement \cite{Rezaei2016}. The
pair-counting measures applied are \textit{rand index} (RI - agreement
probability), \textit{adjusted rand index} (ARI), \textit{mirkin's index} (MI -
disagreement probability), and \textit{hubert's index} (HI - $(P(agree)$ -
$P(disagree))$) \cite{Hubert1985, Meila2003}. When comparing ground truth labels
to cluster assignments, RI can serve as an estimation of the accuracy. ARI is
similar to the RI, though it is corrected for chance and thus does not count
randomly generated labels \cite{Rand1971}.

\begin{figure}[ht]
      \centering
      \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\linewidth]{salinasgt.png}
            \caption{Salinas-A Ground Truth}
            \label{fig:salinasgt}
      \end{subfigure}
      \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\linewidth]{risodata.png}
            \caption{Random Centers (ARI=0.797)}
            \label{fig:salinasr}
      \end{subfigure}\hfill
      \centering
      \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\linewidth]{kisodata.png}
            \caption{KM++ Centers (ARI=0.781)}
            \label{fig:salinask}
      \end{subfigure}
      \begin{subfigure}[b]{0.4\textwidth}
            \centering
            \includegraphics[width=\linewidth]{iisodata.png}
            \caption{ISODS Centers (ARI=0.758)}
            \label{fig:salinasi}
      \end{subfigure}\hfill \caption{Heatmap showing cluster assignments of each
            pixel using ISODATA with different initial cluster center methods.}
      \label{fig:salinas}
\end{figure}

@@

\begin{table}[ht]
      \begin{tabular}{ |p{1.25cm}||p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm}|}
            \hline
            \multicolumn{7}{|c|}{\textbf{ISODATA} - \textit{Salinas-A}}        \\
            \hline
            Init. & Iter. & Clusters & ARI            & RI    & MI    & HI     \\
            \hline
            \multicolumn{7}{|c|}{\textit{Average}}                             \\[1ex]
            ISODS & 2.772 & 2.42     & \textbf{0.156} & 0.388 & 0.612 & -0.224 \\
            KM++  & 3.177 & 1.097    & 0.019          & 0.228 & 0.772 & -0.544 \\
            Rand  & 3.693 & 1.584    & 0.084          & 0.308 & 0.691 & -0.383 \\
            \hline
            \multicolumn{7}{|c|}{\textit{Best}}                                \\[1ex]
            ISODS & 2     & 6        & 0.758          & 0.921 & 0.078 & 0.842  \\
            KM++  & 8     & 6        & 0.781          & 0.930 & 0.070 & 0.860  \\
            Rand  & 14    & 6        & \textbf{0.798} & 0.933 & 0.066 & 0.867  \\
            \hline
      \end{tabular}
      \caption{Salinas-A dataset average and best results over 1000 iterations
            of ISODATA comparing three different initial cluster center
            algorithms (\textit{Init.}). Results in the table contain
            information on iterations required (\textit{Iter.}), number of
            clusters created (\textit{Clusters}), and validity measures.}
      \label{tab:salinastable}
\end{table}

@@

\section{Conclusion}
This study presents a method for generating initial cluster centers based on a
splitting approach, ISODS. We tested ISODS on bechmark datasets as well as the
Salinas-A hyperspectral image dataset. Both tests on average shows the
performance of ISODS using external cluster validation measures, especially on
the \textit{adjusted rand index} measure. Additonally, ISODS may decrease the
number of iterations required for a clustering algorithm such as ISODATA or
K-Means to converge. However, due to the complexity of the ISODS approach,
specifically calculating the means of the clusters, the number of iterations
taken by ISODS should be considered. When used in conjunction with ISODATA,
ISODS also shows an average number of clusters generated closer to the expected
output.

>>>>

\documentclass[a4paper, 10pt]{article}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{abstract}
      \noindent 
      Iterative Self-Organizing Data Analysis Technique (ISODATA) is a
      clustering algorithm based on the K-Means algorithm that intends to find
      the correct number of clusters through merging and splitting. It is
      difficult to determine the correct number of clusters in many real-world
      applications, in particular, remote sensing image interpretation. Compared
      to K-Means, the ISODATA algorithm should be resilient to initial cluster
      centers. However, ISODATA is also sensitive to initial cluster centers
      which impacts the performance of the algorithm. This work proposes using
      the ISODATA approach of splitting clusters to select quality initial
      cluster centers, called Iterative Self-Organizing Data Split (ISODS). The
      proposed approach is evaluated on several benchmark UCI datasets as well
      as the Salinas-A hyperspectral image dataset. The results are evaluated
      using standard clustering evaluation parameters. When ISODS is used
      together with ISODATA, the performance is improved and the generated
      clusters more closely resemble the expected number of clusters.\\
      {\bf Keywords :} Clustering, ISODATA, Initial Centroids, Remote Sensing
\end{abstract}

@@

Unsupervised learning is a machine learning technique used when the learning
algorithm has no pre-existing labels and looks for patterns in the data set with
minimum human supervision and without external guidance. In contrast to
supervised learning, where a training set of inputs and observations are given
to the method, unsupervised learning uses only the inputs and should find an
interesting pattern in the data set. Two main approaches are used in
unsupervised learning, named principal component \cite{Mallapragada2018} and
cluster analysis \cite{Xu2015}. In the clustering method, unlabeled and unsorted
data points are grouped and segmented according to similarities and differences
to find structure in the inputs, group it into meaningful clusters, and
understand the data set better. There are different algorithms for Clustering,
such as K-Means \cite{Lloyd1982,Macqueen1967}, fuzzy C-Means, ISODATA
\cite{Ball1965}, and so on. In the K-Means algorithm, the goal is to minimize
the sum of the squared distances points have in the data set from its center.
The problem with the K-Means algorithm is that it requires a priori knowledge
about the number of classes in the data set, and choosing the cluster centers
randomly may not result in optimal partitioning of the data set.

@@

The K-Means algorithm is an unsupervised clustering algorithm and aims to
partition $N$ observations into $K$ clusters \cite{Lloyd1982,Macqueen1967}. Data
points in the same cluster are very similar to each other and have less
variation compared to data points assigned to other clusters. The user defines
$K$, the number of expected clusters. Following is a description of the K-Means
algorithm:

@@

For selecting the initial cluster centers in \textbf{Step 1}, there are two
standard methods: Random Centers, and K-Means++ \cite{Arthur2007}. In Random
Centers, $K$ samples are randomly chosen from the dataset to serve as the
initial cluster centers. In K-Means++, $1$ sample is randomly chosen from the
dataset to serve as the initial cluster center. Then, $K-1$ samples are
iteratively selected, where the probability of a sample being chosen as a
cluster center is the distance of the sample from previously chosen centers
\cite{Arthur2007}. The K-Means algorithm is susceptible to initial starting
cluster centers, where different initial values can result in a different
classification \cite{Franti2018}.

@@

ISODATA is another frequently used clustering algorithm and is based on the
K-Means algorithm \cite{Ball1965}. Like K-Means, cluster centers are iteratively updated and
reassigned to the samples in the dataset. However, ISODATA determines the number
of clusters dynamically and allows for a different number of cluster centers. In
contrast, the K-Means algorithm requires a fixed user-set parameter of the
number of expected clusters. The advantage found within ISODATA allows for
discovery of a different number of clusters, which is achieved through
discarding clusters with a small number of member samples, and merging and
splitting clusters that meet certain parameters. There are three main ISODATA
parameters:

@@

There are some disadvantages to the ISODATA algorithm. First, it is sensitive to
the parameters $\theta n$, $\theta e$, and $\theta c$. These parameters should
be fine-tuned for optimal performance based on the attributes of the dataset
being tested. In addition, similar to K-Means, it is sensitive to initial
cluster centers, although less so than K-Means due to the extra processes of
discarding, splitting, and merging. The initial centroids can affect both the
quality of clusters produced and the number of iterations required to converge
\cite{Franti2018}.

@@

\begin{itemize}
      \item \textbf{Step 1:} Choose one observation as a cluster center from the
            dataset.
      \item \textbf{Step 2:} Assign each element of the dataset to the cluster
            based on the minimum distance from the cluster center.
      \item \textbf{Step 3:} Re-calculate new cluster centers for each cluster
            by computing the mean of all patterns assigned to each cluster.
      \item \textbf{Step 4:} If the number of clusters is equal to $K$, then the
            process is terminated. If the number of clusters is greater than
            $K$, then the clusters with the fewest members is discarded, and the
            algorithm moves to \textbf{Step 2}.
      \item \textbf{Step 5:} Calculate the standard deviation of each cluster in
            each dimension. Then, split each cluster along the dimension with
            the greatest standard deviation and move to \textbf{Step 2}.
\end{itemize}

@@

@@

To evaluate the cluster results, external cluster validation measures are used.
We utilize pair-counting measures which rely on counting matching pairs between
two sets of data to determine agreement and disagreement \cite{Rezaei2016}. The
pair-counting measures applied are \textit{Rand index} (RI - agreement
probability), \textit{adjusted Rand index} (ARI), \textit{Mirkin's index} (MI -
disagreement probability), and \textit{Hubert's index} (HI - $(P(agree)$ -
$P(disagree))$) \cite{Hubert1985, Meila2003}. When comparing ground truth labels
to cluster assignments, RI can serve as an estimation of the accuracy. ARI is
similar to the RI, though it is corrected for chance and thus does not count
randomly generated labels \cite{Rand1971}.

The ISODATA algorithm does not have a determined number of clusters to generate.
Instead, the user sets the max clusters desired, and the algorithm will generate
a number of clusters between and the max and half the max number desired. Since
the output depends on the data, the ISODATA parameters, and the initial centers,
we include a column to depict the average number of clusters.

\begin{table}[ht]
      \caption{UCI benchmark dataset results averaged over 1000 iterations of
            ISODATA comparing three different initial cluster center algorithms
            (\textit{Init.}). ARI - adjusted Rand index; RI - Rand index; MI -
            Mirkin's index; HI - Hubert's index.}
      \begin{tabular}{ |p{1.25cm}||p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm}|}
            \hline
            \multicolumn{7}{|c|}{\textbf{ISODATA}}                               \\
            \hline
            Init. & Iter.  & Clusters & ARI             & RI    & MI    & HI     \\
            \hline
            \multicolumn{7}{|c|}{\textit{Iris}}                                  \\
            \hline
            ISODS & 13.46  & 2.599    & \textbf{0.646}  & 0.826 & 0.173 & 0.653  \\
            KM++  & 15.43  & 2.544    & 0.628           & 0.816 & 0.184 & 0.631  \\
            Rand  & 11.90  & 2.41     & 0.607           & 0.802 & 0.198 & 0.604  \\
            \hline
            \multicolumn{7}{|c|}{\textit{Glass (Normalized)}}                    \\
            \hline
            ISODS & 3.19   & 1.066    & \textbf{0.0018} & 0.266 & 0.734 & -0.468 \\
            KM++  & 4.02   & 1.028    & 0.0011          & 0.265 & 0.735 & -0.470 \\
            Rand  & 3.69   & 1.055    & 0.0013          & 0.266 & 0.733 & -0.467 \\
            \hline
            \multicolumn{7}{|c|}{\textit{Wine}}                                  \\
            \hline
            ISODS & 9.16   & 1.836    & \textbf{0.313}  & 0.618 & 0.382 & 0.236  \\
            KM++  & 8.76   & 1.816    & 0.307           & 0.612 & 0.388 & 0.224  \\
            Rand  & 9.26   & 1.810    & 0.304           & 0.608 & 0.391 & 0.217  \\
            \hline 
            \multicolumn{7}{|c|}{\textbf{K-Means}}                               \\
            \hline
            \multicolumn{7}{|c|}{\textit{Iris}}                                  \\
            \hline
            ISODS & 2.29   & 3        & \textbf{0.623}  & 0.833 & 0.167 & 0.667  \\
            KM++  & 4.149  & 3        & 0.584           & 0.811 & 0.189 & 0.621  \\
            Rand  & 29.402 & 3        & 0.569           & 0.797 & 0.203 & 0.593  \\
            \hline
            \multicolumn{7}{|c|}{\textit{Glass (Normalized)}}                    \\
            \hline
            ISODS & 5.651  & 6        & 0.164           & 0.665 & 0.335 & 0.329  \\
            KM++  & 4.866  & 6        & \textbf{0.173}  & 0.643 & 0.357 & 0.285  \\
            Rand  & 77.178 & 6        & 0.151           & 0.634 & 0.366 & 0.268  \\
            \hline
            \multicolumn{7}{|c|}{\textit{Wine}}                                  \\
            \hline
            ISODS & 3.145  & 3        & \textbf{0.882}  & 0.947 & 0.053 & 0.895  \\
            KM++  & 5.388  & 3        & 0.839           & 0.926 & 0.074 & 0.851  \\
            Rand  & 24.775 & 3        & 0.834           & 0.920 & 0.080 & 0.840  \\
            \hline
      \end{tabular}
      \label{tab:ucitable}
\end{table}

@@

\begin{table}[ht]
      \caption{Salinas-A dataset average and best results over 1000 iterations
            of ISODATA comparing three different initial cluster center
            algorithms (\textit{Init.}).}
      \begin{tabular}{ |p{1.25cm}||p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm}|}
            \hline
            \multicolumn{7}{|c|}{\textbf{ISODATA} - \textit{Salinas-A}}        \\
            \hline
            Init. & Iter. & Clusters & ARI            & RI    & MI    & HI     \\
            \hline
            \multicolumn{7}{|c|}{\textit{Average}}                             \\
            \hline
            ISODS & 2.772 & 2.42     & \textbf{0.156} & 0.388 & 0.612 & -0.224 \\
            KM++  & 3.177 & 1.097    & 0.019          & 0.228 & 0.772 & -0.544 \\
            Rand  & 3.693 & 1.584    & 0.084          & 0.308 & 0.691 & -0.383 \\
            \hline
            \multicolumn{7}{|c|}{\textit{Best}}                                \\
            \hline
            ISODS & 2     & 6        & 0.758          & 0.921 & 0.078 & 0.842  \\
            KM++  & 8     & 6        & 0.781          & 0.930 & 0.070 & 0.860  \\
            Rand  & 14    & 6        & \textbf{0.798} & 0.933 & 0.066 & 0.867  \\
            \hline
      \end{tabular}
      \label{tab:salinastable}
\end{table}

\begin{figure}[ht]
      \centering
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{salinasgt.png}
            \label{fig:salinasgt}
      \end{subfigure}
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{risodata.png}
            \label{fig:salinasr}
      \end{subfigure}
      \centering
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{kisodata.png}
            \label{fig:salinask}
      \end{subfigure}
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{iisodata.png}
            \label{fig:salinasi}
      \end{subfigure}\hfill \caption{Heatmap showing cluster assignments of each
            pixel using ISODATA with different initial cluster center methods.
            (a) Salinas-A Ground Truth; (b) Random Centers (ARI=0.797); KM++
            Centers (ARI=0.781); ISODS Centers (ARI=0.758).}
      \label{fig:salinas}
\end{figure}

@@

\section{Conclusion}
This study presents a method for generating initial cluster centers based on a
splitting approach, Iterative Self-Organizing Data Split (ISODS). We tested ISODS on
bechmark datasets as well as the Salinas-A hyperspectral image dataset. Both
tests on average shows the performance of ISODS using external cluster
validation measures, especially on the \textit{adjusted Rand index} measure.
Additonally, ISODS may decrease the number of iterations required for a
clustering algorithm such as ISODATA or K-Means to converge. However, due to the
complexity of the ISODS approach compared to other initial centroid algorithms,
specifically calculating the means of the clusters, the context should be
considered when applying this method. When used in conjunction with ISODATA,
ISODS shows an average number of clusters generated closer to the expected
output.
